---
title: "Likeliness to Recommend to a Friend or Colleague"
output:
  rmdformats::robobook:
    self_contained: true # Other options are downcute, material, readthedown, html_clean, html_docco, lockdown, https://github.com/juba/rmdformats
    thumbnails: false
    lightbox: true
    gallery: false
    highlight: kate # Also can do tango
    number_sections: false
    includes:
      after_body: footer.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, 
                      message = F, 
                      warning = F, 
                      fig.align = 'center', 
                      cache = F, 
                      tidy = T) # No messages, warnings, code echo, align figures center, cache images, and tidy
library(tidyverse) # So you don't have to code in base R
library(hrbrthemes) # For pretty graphing themes
library(readr) # Reading in rds
library(here) # Cross network consistency
library(scales) # For graphing scales
library(ggrepel) # For text output on graphs
theme_set(theme_minimal())
teaching_colors <- c("#04ABEB", "#040404", "#346475", "#324D56") # Teaching Lab Color Palette - derived from logo
col = grDevices::colorRampPalette(c("#040404", "#04ABEB")) # Color palette maker for blue theme, based on teaching lab color palette
htmltools::tagList(rmarkdown::html_dependency_font_awesome()) # Needed so fa's in footer will show
```

```{r}
teaching_df <- read_rds(here("Data/final_df.rds")) # Read in the data
teaching_lab_df <- read_rds(here("Data/original_df.rds")) # Read original data for column names
original_columns <- colnames(teaching_lab_df)
# original_columns # Run if you want to make sure columns match to original data, has to be

# Vector of columns to make factors
cols <- c("professional_training_session", 
          "select_your_site_district_parish_or_network", 
          "select_the_grade_band_s_you_focused_on", 
          "learning_session_satisfaction",
          "todays_topic_was_relevant_for_my_role",
          "designed_to_help_me_learn",
          "likely_to_apply_46_weeks",
          "select_the_name_of_your_first_facilitator",
          "s_he_facilitated_the_content_clearly_12",
          "did_you_have_a_second_facilitator",
          "select_the_name_of_your_second_facilitator",
          "s_he_facilitated_the_content_clearly_16",
          "s_he_effectively_built_a_community_of_learners_17") 

# Columns based on agreement
cols_agree <- c("learning_session_satisfaction", 
                "todays_topic_was_relevant_for_my_role", 
                "designed_to_help_me_learn", 
                "likely_to_apply_46_weeks",
                "s_he_facilitated_the_content_clearly_12",
                "s_he_facilitated_the_content_clearly_16",
                "s_he_effectively_built_a_community_of_learners_17",
                "s_he_effectively_built_a_community_of_learners_13")
```


Which teaching sessions are highest and lowest rated? To find out I plot every single teaching session that has occurred, which results in a lot of plots. Scrolling through all of these is a bit of a hassle but there's really only a couple standouts here, pretty much everything has high scores, except for a couple of the "Guidebooks Diverse Learners", "EL Virtual Bootcamp", "Nebraska Virtual Series", and "IM Bootcamp, Day 2: STRIVE/CPS". I have organized these by the curriculum portfolio, which is titled in between each plot grouping, and highlighted all post-pandemic scores as red for clarity, and finally, arranged the plots by lowest average score for the group. Many of the post-pandemic sessions show up first illustrating a clear score drop in recent times.

# EL

```{r}
# Group and then score the data, filter for the pertinent group
grouped_teaching <- teaching_df %>%
    group_by(professional_training_session, date_for_the_session) %>%
    mutate(count = length(professional_training_session),
           score = sum(likely_to_recommend_colleague_friend)/count) %>%
    ungroup() %>%
  drop_na(professional_training_session) %>%
  dplyr::filter(str_detect(professional_training_session, "EL") == T) %>%# Important filtering part
  arrange(score) # Arrange for plotting
# Loop through each training session per date, and create a column for average score
for (var in unique(grouped_teaching$professional_training_session)) {
  plot_teaching <- grouped_teaching %>%
    dplyr::filter(professional_training_session == var)# Filter for each separate training session before graphing
  # Lollipop graph by date and training session
    plot <- ggplot(plot_teaching, 
                   aes(x = date_for_the_session, y = score)) +
      ggplot2::ylim(0, 10) +
      geom_col(position = "dodge", 
               fill = ifelse(plot_teaching$date_for_the_session >= as.Date("2020-04-01"), 
                             "red3", 
                             "#04ABEB"),
               color = ifelse(plot_teaching$date_for_the_session >= as.Date("2020-04-01"), 
                             "red3", 
                             "#04ABEB"),
               width = 1) +
      geom_point(color = "black") +
        geom_hline(linetype = "F1", 
                   color = "black", 
                   aes(yintercept = 8.913986)) +
        geom_text(aes(label = "Mean likeliness\n to recommend to a\n colleague or friend", 
                      x = as.Date("2020-05-01"), 
                      y = 10), 
                  color = "black",
                  size = 2) + 
      geom_segment(aes(x = as.Date("2020-05-01"), y = 9.5, xend = as.Date("2020-05-01"), yend = 9), 
                   arrow = arrow(length = unit(0.05, "cm"))) +
      ggtitle(paste(var)) +
      labs(x = "Date", y = "Group Likeliness to Recommend to Colleague or Friend") +
      scale_x_date(date_labels = "%b %Y", limits = c(as.Date("2019-06-05"), Sys.Date())) +
      theme(legend.position = "none",
            plot.title = element_text(hjust = 0.5))
    print(plot)
}
```

# Guidebooks

```{r}
# There's Guidebooks, and GuideBooks so vector for later filter
guidebooks <- c("Guidebooks|GuideBooks")
# Group and then score the data, filter for the pertinent group
grouped_teaching <- teaching_df %>%
    group_by(professional_training_session, date_for_the_session) %>%
    mutate(count = length(professional_training_session),
           score = sum(likely_to_recommend_colleague_friend)/count) %>%
    ungroup() %>%
  drop_na(professional_training_session) %>%
  dplyr::filter(str_detect(professional_training_session, guidebooks) == T) %>%# Important filtering part
  arrange(score) # Arrange for plotting
# Loop through each training session per date, and create a column for average score
for (var in unique(grouped_teaching$professional_training_session)) {
  plot_teaching <- grouped_teaching %>%
    dplyr::filter(professional_training_session == var)# Filter for each separate training session before graphing
  # Lollipop graph by date and training session
    plot <- ggplot(plot_teaching, 
                   aes(x = date_for_the_session, y = score)) +
      ggplot2::ylim(0, 10) +
      geom_col(position = "dodge", 
               fill = ifelse(plot_teaching$date_for_the_session >= as.Date("2020-04-01"), 
                             "red3", 
                             "#04ABEB"),
               color = ifelse(plot_teaching$date_for_the_session >= as.Date("2020-04-01"), 
                             "red3", 
                             "#04ABEB"),
               width = 1) +
      geom_point(color = "black") +
        geom_hline(linetype = "F1", 
                   color = "black", 
                   aes(yintercept = 8.913986)) +
        geom_text(aes(label = "Mean likeliness\n to recommend to a\n colleague or friend", 
                      x = as.Date("2020-05-01"), 
                      y = 10), 
                  color = "black",
                  size = 2) + 
      geom_segment(aes(x = as.Date("2020-05-01"), y = 9.5, xend = as.Date("2020-05-01"), yend = 9), 
                   arrow = arrow(length = unit(0.05, "cm"))) +
      ggtitle(paste(var)) +
      labs(x = "Date", y = "Group Likeliness to Recommend to Colleague or Friend") +
      scale_x_date(date_labels = "%b %Y", limits = c(as.Date("2019-06-05"), Sys.Date())) +
      theme(legend.position = "none",
            plot.title = element_text(hjust = 0.5))
    print(plot)
}
```

# Illustrative Mathematics (IM)

```{r}
# Group and then score the data, filter for the pertinent group
grouped_teaching <- teaching_df %>%
    group_by(professional_training_session, date_for_the_session) %>%
    mutate(count = length(professional_training_session),
           score = sum(likely_to_recommend_colleague_friend)/count) %>%
    ungroup() %>%
  drop_na(professional_training_session) %>%
  dplyr::filter(str_detect(professional_training_session, "IM") == T) %>%# Important filtering part
  arrange(score) # Arrange for plotting
# Loop through each training session per date, and create a column for average score
for (var in unique(grouped_teaching$professional_training_session)) {
  plot_teaching <- grouped_teaching %>%
    dplyr::filter(professional_training_session == var)# Filter for each separate training session before graphing
  # Lollipop graph by date and training session
    plot <- ggplot(plot_teaching, 
                   aes(x = date_for_the_session, y = score)) +
      ggplot2::ylim(0, 10) +
      geom_col(position = "dodge", 
               fill = ifelse(plot_teaching$date_for_the_session >= as.Date("2020-04-01"), 
                             "red3", 
                             "#04ABEB"),
               color = ifelse(plot_teaching$date_for_the_session >= as.Date("2020-04-01"), 
                             "red3", 
                             "#04ABEB"),
               width = 1) +
      geom_point(color = "black") +
        geom_hline(linetype = "F1", 
                   color = "black", 
                   aes(yintercept = 8.913986)) +
        geom_text(aes(label = "Mean likeliness\n to recommend to a\n colleague or friend", 
                      x = as.Date("2020-05-01"), 
                      y = 10), 
                  color = "black",
                  size = 2) + 
      geom_segment(aes(x = as.Date("2020-05-01"), y = 9.5, xend = as.Date("2020-05-01"), yend = 9), 
                   arrow = arrow(length = unit(0.05, "cm"))) +
      ggtitle(paste(var)) +
      labs(x = "Date", y = "Group Likeliness to Recommend to Colleague or Friend") +
      scale_x_date(date_labels = "%b %Y", limits = c(as.Date("2019-06-05"), Sys.Date())) +
      theme(legend.position = "none",
            plot.title = element_text(hjust = 0.5))
    print(plot)
}
```

# State-level work

```{r}
not_state_level <- c("EL|IM|Guidebooks|GuideBooks") # Define those for which we should filter for later
# Group and then score the data, filter for the pertinent group
grouped_teaching <- teaching_df %>%
    group_by(professional_training_session, date_for_the_session) %>%
    mutate(count = length(professional_training_session),
           score = sum(likely_to_recommend_colleague_friend)/count) %>%
    ungroup() %>%
  drop_na(professional_training_session) %>%
  dplyr::filter(!str_detect(professional_training_session, not_state_level)) %>% # Filter for State level work
  arrange(score) # Arrange for plotting
# Loop through each training session per date, and create a column for average score
for (var in unique(grouped_teaching$professional_training_session)) {
  plot_teaching <- grouped_teaching %>%
    dplyr::filter(professional_training_session == var)# Filter for each separate training session before graphing
  # Lollipop graph by date and training session
    plot <- ggplot(plot_teaching, 
                   aes(x = date_for_the_session, y = score)) +
      ggplot2::ylim(0, 10) +
      geom_col(position = "dodge", 
               fill = ifelse(plot_teaching$date_for_the_session >= as.Date("2020-04-01"), 
                             "red3", 
                             "#04ABEB"),
               color = ifelse(plot_teaching$date_for_the_session >= as.Date("2020-04-01"), 
                             "red3", 
                             "#04ABEB"),
               width = 1) +
      geom_point(color = "black") +
        geom_hline(linetype = "F1", 
                   color = "black", 
                   aes(yintercept = 8.913986)) +
        geom_text(aes(label = "Mean likeliness\n to recommend to a\n colleague or friend", 
                      x = as.Date("2020-05-01"), 
                      y = 10), 
                  color = "black",
                  size = 2) + 
      geom_segment(aes(x = as.Date("2020-05-01"), y = 9.5, xend = as.Date("2020-05-01"), yend = 9), 
                   arrow = arrow(length = unit(0.05, "cm"))) +
      ggtitle(paste(var)) +
      labs(x = "Date", y = "Group Likeliness to Recommend to Colleague or Friend") +
      scale_x_date(date_labels = "%b %Y", limits = c(as.Date("2019-06-05"), Sys.Date())) +
      theme(legend.position = "none",
            plot.title = element_text(hjust = 0.5))
    print(plot)
}
```

