---
title: "Pie Chart Maker"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = F, 
                      message = F, 
                      warning = F, 
                      fig.align = 'center', 
                      cache = F, 
                      tidy = T) # No messages, warnings, code echo, align figures center, cache images, and tidy
library(tidyverse)
library(here)
library(scales) # For graphing scales
library(shiny)
library(DT)
library(grDevices)
teaching_colors <- c("#04ABEB", "#040404", "#346475", "#324D56") # Teaching Lab Color Palette - derived from logo
col = grDevices::colorRampPalette(c("#040404", "#04ABEB")) # Color palette maker for blue theme, based on teaching lab color palette
```

```{r}
teaching_df <- read_rds(here("Data/final_df.rds")) # Read in the data
teaching_lab_df <- read_rds(here("Data/original_df.rds")) # Read original data for column names
original_columns <- colnames(teaching_lab_df)
# original_columns # Run if you want to make sure columns match to original data, has to be

# Vector of columns to make factors
cols <- c("professional_training_session", 
          "select_your_site_district_parish_or_network", 
          "select_the_grade_band_s_you_focused_on", 
          "learning_session_satisfaction",
          "todays_topic_was_relevant_for_my_role",
          "designed_to_help_me_learn",
          "likely_to_apply_46_weeks",
          "select_the_name_of_your_first_facilitator",
          "s_he_facilitated_the_content_clearly_12",
          "did_you_have_a_second_facilitator",
          "select_the_name_of_your_second_facilitator",
          "s_he_facilitated_the_content_clearly_16",
          "s_he_effectively_built_a_community_of_learners_17") 

# Columns based on agreement
cols_agree <- c("learning_session_satisfaction", 
                "todays_topic_was_relevant_for_my_role", 
                "designed_to_help_me_learn", 
                "likely_to_apply_46_weeks",
                "s_he_facilitated_the_content_clearly_12",
                "s_he_facilitated_the_content_clearly_16",
                "s_he_effectively_built_a_community_of_learners_17",
                "s_he_effectively_built_a_community_of_learners_13")
```

Making a circle chart for each factor using a function, this could also be done with a for loop or purrr::map(), but I assume you want to look at a specific variable if you are using this most of the time. I know this isn't super pretty but Shiny gets pretty complicated when you try to make it look good and I think this is deciperable at the least. Each possible option is provided below:

```{r}
selectInput("data", cols, width = '600px',
            label = h3("Select Variable:")) # Basic Shiny Input Take
```


```{r cache = F, eval = F}
# Original function I wrote that has to be implemented differently for shiny when taking input it has to be called to a reactive first,
# so it can have defineable columns to read, and the string input to pieCharter is indecipherable to renderPlot for some reason
pieCharter <- function(variable) {
    plot_data <- teaching_df %>%
          dplyr::group_by({{variable}}) %>% # Group by input variable
          dplyr::summarise(n = n()) %>% # Get count of variable
          ungroup() %>% # Ungroup
          dplyr::mutate(percent = round(100 * (n / sum(n)), 2)) # Make a percent column
    plot <- ggplot(plot_data, aes(x = 0, y = n, fill = reorder({{variable}}, n))) + #Pie chart input, ordered by n
          labs(fill = "Type", x = NULL, y = NULL, 
               title = paste("Percentage of", colnames(plot_data)[1]), 
               subtitle = "Variables with greater than 5% occurrence") +
          geom_bar(stat = "identity", color = "gray", width = 0.5) + # Using bar columns put in polar coordinates later
          geom_text(aes(label = ifelse(percent > 5, 
                                       paste0(percent, "%\n", {{variable}}), 
                                       paste("")),
                        x = 0.4), 
                    position = position_stack(vjust = 0.5), #position stack normally stacks bars, but here it keeps the text in the right place once put in polar
                    size = 3,
                    fontface = "bold") + # Add bold text with percentage and variable label
          scale_x_continuous(expand = c(0, 0)) + # Change x so expand is not default and adds no padding so the bars will produce a circle not a donut
          coord_polar(theta = "y", direction = -1) + # Make bars polar
          scale_fill_manual(values = c(col(nrow(plot_data)))) + # custom colors
          theme_void() + # Remove all panel elements
          theme(legend.position = "none",
                plot.title = element_text(hjust = 0.5),
                plot.subtitle = element_text(hjust = 0.5))
          print(plot)
}
```


Plot will render here:

```{r cache = F}
mydata <- reactive({
  teaching_df %>%
          dplyr::group_by(get(input$data)) %>% # Group by input variable
          dplyr::summarise(n = n()) %>% # Get count of variable
          ungroup() %>% # Ungroup
          dplyr::mutate(percent = round(100 * (n / sum(n)), 2)) # Make a percent column
})

renderPlot({
  # ggplot2::ggplot(mydata(), aes(x = 0, y = n, fill = reorder(`get(input$data)`, n))) + #Pie chart input, ordered by n
  #         labs(fill = "Type", x = NULL, y = NULL,
  #              title = paste("Percentage of", as.character(input$data),
  #              subtitle = "Variables with greater than 5% occurrence")) +
  #         geom_bar(stat = "identity", color = "gray", width = 0.5)
  
  ggplot2::ggplot(mydata(), aes(x = 0, y = n, fill = reorder(`get(input$data)`, n))) + #Pie chart input, ordered by n
          labs(fill = "Type", x = NULL, y = NULL,
               title = paste("Percentage of", as.character(input$data)),
               subtitle = "Variables with greater than 5% occurrence") +
          geom_bar(stat = "identity", color = "gray", width = 0.5) + # Using bar columns put in polar coordinates later
          geom_text(aes(label = ifelse(percent > 5,
                                       paste0(percent, "%\n", as.character(`get(input$data)`)),
                                       paste("")),
                        x = 0.4),
                    position = position_stack(vjust = 0.5), #position stack normally stacks bars, but here it keeps the text in the right place once put in polar
                    size = 3,
                    fontface = "bold") + # Add bold text with percentage and variable label
          scale_x_continuous(expand = c(0, 0)) + # Change x so expand is not default and adds no padding so the bars will produce a circle not a donut
          coord_polar(theta = "y", direction = -1) + # Make bars polar
          scale_fill_manual(values = c(col(nrow(mydata())))) + # custom colors
          theme_void() + # Remove all panel elements
          theme(legend.position = "none",
                plot.title = element_text(hjust = 0.5),
                plot.subtitle = element_text(hjust = 0.5))
})
```

A table will render here:

```{r}
DT::renderDT({
  DT::datatable(mydata(), colnames = c(paste(str_to_title(input$data), "Group"), "Number", "Percent"))
})

renderText({ 
    paste("You have selected", str_to_title(input$data))
  })
```





```{r cache = F}
# pieCharter(variable = professional_training_session)
# pieCharter(variable = select_your_site_district_parish_or_network)
# pieCharter(variable = select_the_grade_band_s_you_focused_on)
# pieCharter(variable = learning_session_satisfaction)
# pieCharter(variable = todays_topic_was_relevant_for_my_role)
# pieCharter(variable = designed_to_help_me_learn)
# print(pieCharter(variable = likely_to_apply_46_weeks))
# pieCharter(variable = select_the_name_of_your_first_facilitator)
# pieCharter(variable = s_he_facilitated_the_content_clearly_12)
# pieCharter(variable = did_you_have_a_second_facilitator)
# pieCharter(variable = select_the_name_of_your_second_facilitator)
# pieCharter(variable = s_he_facilitated_the_content_clearly_16)
# pieCharter(variable = s_he_effectively_built_a_community_of_learners_17)

# teaching_df %>%
#   {map2(list(.), names(teaching_df[cols]), ~ pieCharter)}
# Wanted to map this, really hard for some reason not worth the time to figure out, for some reason ggplot output is weird with map
```








